### 2014-02-25 paper/retrofit.tex
Restructure the rules a little bit.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

While we would like to add information flow control to \emph{any}
language, we will have to make some assumptions about the form of the
target language.  We consider languages whose semantics can be expressed
in the form of abstract machines |(tS, tE, te, ->)|, where |tS| is the
global machine state, |tE| is an evaluation context, |te| is an
expression in the language and |->| is the reduction relation on such
configuration, i.e., $|->| : (|tS| \times |tE| \times |te|)
\rightharpoonup (|tS| \times |tE| \times |te|)$.  Metavariables in this
target language have been colored red.

In Figure~\ref{fig:ml}, we give an example of a standard ML-like
language with mutable references.  These semantics have been prepared
for interoperability in the style of Matthews and Findler~\nocite{}, in
particular, the evaluation rules have been expressed in terms of an
evaluation context $\mathcal{E}_{\tar{\Sigma}}$.  Without the embedding,
this evaluation context is defined as |conf tS te @= tS, tE[ te ]|, but
when we perform the embedding, we will reinterpret the meaning
of this operator, moving .

@@

\begin{figure}
Typing judgment: $|tyrule tG tS te tty|$
\begin{mathpar}
\inferrule[T-ty-address]
{}
{| tyrule tG tS a (ref (tyLookup tS a)) |}
\end{mathpar}

\caption{Selected typing rules for ML-like language}
\label{fig:ml-typing}
\end{figure}

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit | IT tv
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie |  IT te
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie |  IT tE
io   ::=  (il, id ie)
Q    ::=  nil | io , Q

te   ::=  cdots | TI ie
tE   ::=  cdots | TI iE

ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)

conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
\end{code}
\caption{IFC grammar.}
\label{fig:ifc-grammar}
\end{figure}

\begin{figure}
\begin{mathpar}
\and
\inferrule[I-done]
{|
|}
{|
iconf iS (fullconf id il tS iv, ldots)
.->
iS ; sched done (fullconf id il tS iv, ldots)
|}

@@

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
.->
iS'; sched fork (it1, ldots, itnew)
|}

@@

\inferrule[I-labelOp]
{ |denot (il1 lop il2) = iv|}
{ |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }

@@

\and
\inferrule[T-border]
{ } {| conf tS (TI (IT (te))) -> conf tS te|}
\end{mathpar}
\caption{IFC language and general embedding.}
\label{fig:ifc}
\end{figure}

>>>>

While we would like to add information flow control to \emph{any}
language, we will have to make some assumptions about the form of the
target language.  We consider languages whose semantics can be expressed
in the form of abstract machines |(tS, tE, te, tv, ->)|, where |tS| is the
global machine state, |tE| is an evaluation context, |te| is an
expression in the language, |tv| is the set of values, and |->| is the reduction relation on such
configuration, i.e., $|->| : (|tS| \times |tE| \times |te|)
\rightharpoonup (|tS| \times |tE| \times |te|)$.  Metavariables in this
target language have been colored red.

In Figure~\ref{fig:ml}, we give an example of a standard ML-like
language with mutable references.  These semantics have been prepared
for interoperability in the style of Matthews and Findler~\Red{XXX}; in
particular, the evaluation rules have been expressed in terms of an
evaluation context $\mathcal{E}_{\tar{\Sigma}}$.  Without the embedding,
this evaluation context is defined as |conf tS te @= tS, tE[ te ]|, but
when we perform the embedding, we will reinterpret the meaning
of this evaluation context, lifting these semantics to an IFC setting.

@@

%   \begin{figure}
%   Typing judgment: $|tyrule tG tS te tty|$
%   \begin{mathpar}
%   \inferrule[T-ty-address]
%   {}
%   {| tyrule tG tS a (ref (tyLookup tS a)) |}
%   \end{mathpar}

%   \caption{Selected typing rules for ML-like language}
%   \label{fig:ml-typing}
%   \end{figure}

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie
io   ::=  (il, id ie)
Q    ::=  nil | io , Q

CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
\end{code}

\begin{mathpar}
%   \and
%   \inferrule[I-done]
%   {|
%   |}
%   {|
%   iconf iS (fullconf id il tS iv, ldots)
%   .->
%   iS ; sched done (fullconf id il tS iv, ldots)
%   |}

@@

@@

\inferrule[I-labelOp]
{ |denot (il1 lop il2) = iv|}
{ |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }
\end{mathpar}
\caption{IFC language}
\label{fig:ifc}
\end{figure}

\begin{figure}
\begin{tabular}{ll}
\begin{minipage}{.22\textwidth}
\begin{code}
iv ::= cdots | IT tv
ie ::= cdots | IT te
iE ::= cdots | IT tE
\end{code}
\end{minipage} &
\begin{minipage}{.22\textwidth}
\begin{code}
tv ::= cdots | TI iv
te  ::=  cdots | TI ie
tE   ::=  cdots | TI iE
\end{code}
\end{minipage}
\end{tabular}

\begin{code}
ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)

conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
\end{code}

\begin{mathpar}
\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
.->
iS'; sched fork (it1, ldots, itnew)
|}

@@

\and
\inferrule[T-border]
{ } {| conf tS (TI (IT (te))) -> conf tS te|}
\end{mathpar}
\caption{The embedding}
\label{fig:embedding-grammar}
\end{figure}
